\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Full-Stack Web Developer \hfill Summer 2021}}
\subtext{Praxes Medical Group \hfill Halifax, NS}
\begin{zitemize}
\item Maintained and updated their serverless COVID testing software for public rapid testing sites and B2B employer-led testing; facilitated the reporting of 300,000+ test results to patients, as well as aggregate statistic reports to stakeholders.
\item Redesigned their database scheme to allow more performant result querying and storage of additional information about tests.
\item Designed and implemented a database, serverless backend, and Vue.js web app for volunteer registration and cancellation.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Assistant to the Support Engineers \hfill Summer 2019}}
\subtext{SolutionInc \hfill Halifax, NS}
\begin{zitemize}
\item Assembled single-board computers, automated software staging, and performed quality assurance testing, in order to allow secure media casting from user devices in some of the world's leading hotels.
\item Staged wireless access points for various hotels, campgrounds, convention centers, etc., to run network gateway software.
\item Applied testing and troubleshooting skills to resolve connectivity issues for clients and provide exceptional customer service.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Technology \& Service Coordinator  \hfill 2017, 2018, 2020, 2022}}
\subtext{Race Auto Group \hfill Halifax, NS}
\begin{zitemize}
\item Designed and implemented a rental car booking system for the dealership in 2 weeks to capitalize on a local rental car shortage.
\item Responsible for keeping the company website and integrated inventory system up to date.
\item Managed the service desk by creating work orders, ordering parts, resolving customer issues and allocating mechanic time.
\end{zitemize}

\end{document}