\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{SolutionInc Ltd. \hfill 2019, 2023}}
\subtext{Software Developer \hfill Halifax, NS}
\begin{zitemize}
\item Built customer and staff portal applications for a new ISP company. Designed and implemented self-hosted high-availability Kubernetes cluster to host the web portals and services. Automated deployment to staging \& production env's using Helm.
\item Upgraded a legacy LAMPerl-stack network monitoring dashboard to use containers, automated testing, C.I./C.D., \& more. Added a report editing feature to allow customers to customize their hotel/convention center network gateway usage reports.
\item Returned in a software development position after working for a summer on the support \& delivery team as a student, where I mostly worked on staging hardware with proprietary software for allowing secure in-room media casting in large hotel networks.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Praxes Medical Group \hfill 2021}}
\subtext{Software Developer \hfill Halifax, NS}
\begin{zitemize}
\item Maintained and updated their serverless COVID testing software for public rapid testing sites and B2B employer-led testing; facilitated the reporting of 300,000+ test results to patients, as well as aggregate statistic reports to stakeholders.
\item Upgraded Firestore database to allow more performant result querying and storage of additional information about each test.
\item Designed and implemented a serverless backend, database, and Vue.js web app for volunteer registration and cancellation.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Race Auto Group \hfill 2017, 2018, 2020, 2022}}
\subtext{Software Developer, Technology \& Service Coordinator \hfill Halifax, NS}
\begin{zitemize}
\item Rapidly designed and implemented a Next.js rental car booking system for the dealership to capitalize on a local rental car shortage. Later added a custom pricing calendar system, to allow dynamically setting rental rates by date range by vehicle type.
\item Managed the service desk by creating work orders, ordering parts, resolving customer issues, and allocating mechanic time. Was responsible for keeping the company Wordpress website and integrated inventory system up to date.
\end{zitemize}

\end{document}

%====================
% EXPERIENCE D - HIDDEN
%====================
% \subsection{{Assistant to the Support Engineers \hfill Summer 2019}}
% \subtext{SolutionInc \hfill Halifax, NS}
% \begin{zitemize}
% \item Assembled single-board computers, automated software staging, and performed quality assurance testing, in order to allow secure media casting from user devices in some of the world's leading hotels.
% \item Staged wireless access points for various hotels, campgrounds, convention centers, etc., to run network gateway software.
% \item Applied testing and troubleshooting skills to resolve connectivity issues for clients and provide exceptional customer service.
% \end{zitemize}

